A Multi-telescope Campaign on FRB 121102: Implications for the FRB Population

### 2017-07-14 referee_response.txt

Responses start with ">>>"

==================

The authors should tag their DataVerse DOI with the \dataset mark up in AASTeX v6.0

http://journals.aas.org/authors/aastex/aasguide60.html#celestial_objects

Please also use the full references for the items noted under the \software command, e.g.

emcee (Foreman-Mackey et al. 2013)

>>> Done.

=======
Referee Report
Reviewer's Comments:
This paper presents a multi-year observing campaign with the VLA telescope to study the repeating pulses from FRB 121102. Many VLA observations were also simultaneous with observations at radio telescopes observing at other frequencies. In some cases pulses detected at the VLA were not detected at higher or lower frequencies and in one case a pulse was detected with both the VLA and the Arecibo Observatory and this information as well as the pulse spectra from the VLA can be used to constrain the emission properties of this source as well as a burst rate. This work is very interesting, and well-presented, and crucial for our understanding of FRB 121102 in specific, but also the possible properties of fast radio bursts in general.

I think this work is worthy of publication in the journal with moderate revision of the manuscript. Some moderate revision of the text is needed (see below) as well as some structural and conceptual changes. I have included my comments on the manuscript below with general large comments (1, 2, 3..) on the paper at the beginning, and major (A, B, C,...) and minor (i, ii, iii,...) comments per section.

General comments on the manuscript:

1. Throughout the text it is mentioned that this is the first simultaneous detection of an FRB pulse at multiple observatories, but I don't believe this is correct. The observations detailed in Marcote et al. 2017 include VLBI observations of individual pulses from FRB 121102 detected at different observatories. In that sense, this paper does not present the first simultaneous detection. Perhaps the authors mean first simultaneous detection at multiple radio frequencies, but if this is the case this statement should be revised throughout the manuscript.

>>> I do believe the VLA+AO burst is the first of its kind both as a multi-frequency and as a multi-telescope detection. I see two ways to show this:
>>> 1. The first VLA+Arecibo burst was detected on 17 September, while the bursts reported in Marcote et al were detected on 20 September.
>>> 2. Marcote et al was published simultaneously with Chatterjee et al; the latter paper made the first report of this coincident VLA+AO burst.
>>> I would prefer to keep the current wording.

2. While the simultaneous detection of an FRB pulse at multiple frequencies is indeed quite interesting I would argue that the _non-detections_ while observing with the VLA and other telescopes is also extremely important and stick out to me as a key result of this paper. This isn't well highlighted in the abstract or the text of the paper and throughout the manuscript these non-detections are not presented in a straightforward way. The observations are reported as "simultaneous coverage" without mention of detection or non-detection (although non-detection is implied). In a revised version of the manuscript it would be valuable to see these non-detections presented more centrally and directly -- see individual sections for locations where this would be particularly helpful to the reader.

>>> Thank you for helping highlight the most interesting part of the analysis. We will work to raise the profile of the nondetection results.

3. In the text it is written that the Arecibo data are recorded with full Stokes polarization intensity. A bright (39-sigma) pulse was detected at Arecibo in this observing mode but no pulse polarization information is presented here. If pulse polarization information is available for this burst it should absolutely be included in this paper! If for some reason the polarization could not be calibrated or cannot be presented here the reason should be included somewhere in the manuscript.

>>> There is indeed a lot of work to be done on the Arecibo data. That observing campaign is in fact ongoing and multiple students are working on it. We defer detailed Arecibo analysis for future work, as noted here as "Michilli et al, in prep". This paper focused largely on the VLA data analysis and the timing and spectral information derived from comparison to other observatories.

Abstract:

i. "simultaneous observing coverage at other observatories." : Please also mention that these observatories were observing at different radio frequencies and how many VLA pulses were detected and not detected at other observatories.

Introduction:

i. "22 FRBs" : Now 23 with the publication of the ASKAP detection

ii. $0\farcs1$ and $0.01\arcsec$ : Please check for consistency in the placement of the arcseconds symbol throughout the manuscript

Observations:

Figure 1: This figure is very busy and difficult to parse. I would suggest the following changes:
- Change the symbols for each observing epoch to the number of bursts detected in that observation (0, 1, 2, etc)
- Create two extra rows and plot the VLA observations at L-band, S-band, and C-band separately
- Next to the name of each telescope on the right hand side of the figure (or replacing the name of the telescope) provide the observing frequency, e.g. LWA (70 MHz), VLA (1.4 GHz), VLA (3 GHz), VLA (4.5 GHz), etc.
- Use circles to indicate overlapping frequency coverage and dispense with bold circles and dashed lines
- Use a solid line to indicate the observation where a burst was detected at both VLA and Arecibo

Table 1: All times should be in the format HH:MM:SS, e.g. 03:25:29
Table 1: Footnote ordering: Footnotes should be labeled in the order in which they appear, so footnote d should be relabeled as b and so on
Table 1: Footnote wording: This relates to comment #2 at the beginning of this report. I believe it would be better to label these as "detection" and "non-detection" since this is what is implied by "coverage" and the lack of a * icon indicating detection.

2.1 VLA:

A. It would be nice to see the details contained in paragraph 2 of this subsection (as well as the observing setup description paragraphs of other subsections) summarized in a table with information like center observing frequency, bandwidth, time resolution, frequency resolution, dispersion smearing, sensitivity, FWHM, etc.

i. "256 channels" : 256 frequency channels

ii. "prototype version of \textit{realfast}. \textit{realfast} is a" : prototype version of \textit{realfast}, a

iii. "The transient search starts ... and proceeds slower than real-time" : please state how much slower than real-time the search is. If this speed is RFI- or array configuration-dependent provide a range.

2.2 Arecibo:

i. Please include a citation for the PUPPI pulsar backend if there is one.

ii. "Three of those observations ... coverage of VLA bursts and one of those Arecibo observations detected the VLA burst" : This is unclear as it is currently written. It would be better to write up front how many simultaneous observations detected no coincident pulses and how many observations did.

2.3 Effelsberg:

i. Please include a citation for the S60mm receiver if there is one.

ii. Please provide the width of the frequency channels in the Effelsberg setup (in the text and in an observing details table).

2.4 LWA:

i. "Briefly, ..." : Remove this opening word.

ii. "signals" : signal

iii. "Two of the VLA ... had simultaneous coverage with the LWA1" : Here again please be clear about the non-detection with the LWA1.

iv. "up to 48 seconds" : What is the motivation for searching up to 48 seconds in width? Are there physical justifications for searching for such long duration signals in time?

2.5 AMI-LA:

i. "MJDs 57638, ... 57649." : Refer to Figure 1 here.

Results:

It would be nice to see an introductory paragraph before Section 3.1 detailing the main results that will be presented in the following sub-sections: How many VLA pulses were detected in total, how many of those were not detected at other observatories, how many of them were detected at other observatories, what kinds of frequency structure were observed etc. This is a long and complex section of the paper and a preamble might help to guide the reader through the upcoming interesting results.

3.1 Multi-Observatory Burst Spectrum:

Figure 2: Why plot from MJD 57648.437788874842? The justification behind this start time is not given in the text or the caption.
Figure 2: "DM = 560.5 pc $^{-3}$" : missing unit here

Figure 3: Make this figure a little bit bigger so it fills the available column space

3.2 VLA Bursts:

3.2.1 Spectrotemporal Modeling:

Equation 1: A is typically used for a unitless amplitude, but in this case is given in units of flux density. If this value is indeed meant to be the flux density of the pulse then $S$ should be used as the symbol for flux density instead of A.

A. Paragraph beginning "The parameters for the best model ... " : Your fits to the pulse spectra seem to indicate that all but two of the VLA burst detections are well-modeled by a Gaussian envelope completely contained within the 3 GHz band. How likely is this? It seems to be implying that 3 GHz was the perfect frequency at which to center your observations. While this seems fortunate it doesn't make immediate physical sense to me. I might have expected some uniformly broadband pulses, some with an envelope within your observing band, and some with an envelope that extends beyond the observing band, but you find that most are described by an entirely in-band envelope. Is this physical or could this be an artefact of the model fits you have applied to the data? If you believe that this is indeed an intrinsic effect I would like to see more discussion of the physical mechanism behind the very fortunate 3 GHz observing window.

Table 2: Footnote labeling: The labeling here is not consistent with the labeling used in Table 1.

i. "While most bursts are modeled ... into two subbursts." : This particular burst may be an outlier in this sample of bursts but it is not unique among the bursts detected from FRB 121102 which has many bursts that seem to be composed of interesting substructure. A sentence or two putting this particular pulse in that context would be useful.

Figure 4: Are each of the bursts plotted here dedispersed to the best-fit DM given in Table 2 or dedispersed to the best-fit DM of FRB 121102 of 560.5 pc/cm^3? If the former, what effect does it have on the spectrum of each pulse to force them all to a DM = 560.5 pc/cm^3? Is the structure you are seeing in the spectrum highly dependent on the DM fit?

3.2.2 Dispersion:

i. "There is a weak correlation between ... temporal width." : It would be useful information in this section if you could elaborate on how sensitive your observations are or aren't to substructure within each pulse that may be hindering DM fitting? For example, if there was a pulse with substructure within a single 5ms VLA time sample can you estimate the error this would propagate to the DM fit?

3.3 Temporal, Energy, and Brightness Distributions of Bursts:

i. For clarity, please label the rates at different observing frequencies in the text as $R_{3 GHZ}$ etc.

ii. Equation 3: Similar to Equation 1, A is given in units of flux density and should therefore be represented by the symbol $S$.

iii. dN/d logE : Elsewhere in the text this is written as dN/dE. Please be consistent in notation.

Figure 7: Please make this figure larger to fill the available column space. Axis labels and tick labels should be given in a larger font as well.

Discussion:

4.1 Burst Spectra:

A. I do not find the explanation or investigation here into the drastic DM change to be sufficient. The DM is changing (or being measured to change) by many units and disagrees with the best-fit DM at 1.4 GHz. This disagreement between 1.4 GHz and 3 GHz is either intrinsic or extrinsic (or both, I suppose). In the intrinsic case this is of enormous interest. Although an extrinsic explanation would be less physically interesting it would nonetheless provide some helpful answers. Paragraph 6 of this section gives some attention to this issue although it doesn't address the impact that some propagation effects might have on the pulse at different radio frequencies. Given the unique multi-radio-frequency aspect of this work, such a discussion would be valuable. An additional bit of text dedicated to this topic would be illuminating.

i. "We present the first ... to 3.5 GHz." : See comment #1 at the beginning of this report. Statements like these throughout the paper should either be re-worded or removed.

ii. dN/dE : See comment from 3.2.2.

4.3. Flux Distribution:

i. "an lower (redshifted) rate" : a lower (redshifted) rate

4.4 Repetition:

A. A general caution for this section of the manuscript is in applying the lessons of FRB 121102 too widely. There needs to be some caveat in this discussion about how other FRBs have not been seen to repeat, particularly for FRBs that have been followed up as much as FRB 121102. Here you present results from 57 hours of observing with the VLA; some others have been observed for >100 hours without additional pulses and some mention of this should be included here. While indeed at the moment there is no conclusive evidence for multiple sub-populations so it makes sense to generalize a bit, but please also include a statement that not all FRBs might be like this.

i. "day-month" : day-to-month or day and month?

ii. "At the typical Parkes ... at $z \approx 1$" : Please clarify this statement. Do you mean that a Parkes survey could detect the brightest pulse from FRB 121102? The brightest X pulses? The discovery pulse (I think this one was too weak for Parkes)? The "average" pulse?

iii. "understated by a factor of a few by ignoring bursts that fall outside the observing band" : The data presented in this paper are the best currently available to actually constrain this factor. Would it be possible to provide an estimate of this factor using the detections/non-detections from these observations?

iv. "$5 \times 10^2$ and $5 \times 10^3$ times" : Is this range of repetition times sufficient for the repeater? In the observations from just the past 1 year this FRB has emitted O[100] pulses, I believe, and was active at least back to 2012, possibly much longer. Have you or others in the FRB 121102 team attempted to estimate the total number of pulses this FRB may have given off assuming this activity? In doing this does this particular source still fall in the range you've given here? If so, it is worth mentioning where you believe FRB 121102 falls in this range.

Conclusions:

i. "astrophysical source." : astrophysical sources.

ii. "FRB 121102 now serves as a new kind of standard by which FRBs are defined." : In a sense this is true, but this is a very strong statement given the unknown relation between FRB 121102 and the other FRBs that have not been seen to repeat. Please soften or remove this statement.

iii. "That fact, ... about the FRB population." : If they are all the same. I reiterate my caution from Section 4.4 about generalizing this source too much at such an early stage in our understanding of the FRB population.

iv. dN/dE : See comment from 3.2.2

### 2017-07-14 repeater-vladata.tex
fixed aastex bug
adding mattthew a acknowledgements
bumping up the nondetection coverage

\documentclass[twocolumn]{aastex61}
%\documentclass{emulateapj}
\usepackage{hyperref} 
\usepackage{graphicx,natbib}
\citestyle{aa}
\usepackage[space]{grffile}
\usepackage{latexsym}
\usepackage{amsfonts,amsmath,amssymb}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage{fancyref}
\usepackage{multirow}
\hypersetup{colorlinks=false,pdfborder={0 0 0},}

@@

\title{A Multi-telescope Campaign on \frb: Implications for the FRB Population}
\shorttitle{\frb\ Observing Campaign}
\shortauthors{Law et al.}

@@

\begin{abstract}
We present results of the coordinated observing campaign that made the first subarcsecond localization of a Fast Radio Burst, \frb. During this campaign, we made the first simultaneous detection of an FRB burst by multiple telescopes: the VLA at 3~GHz and the Arecibo Observatory at 1.4~GHz. Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories. We use multi-observatory constraints and modeling of bursts seen only at 3~GHz to confirm earlier results showing that burst spectra are not well modeled by a power law. We find that burst spectra are characterized by a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg. We measure significant changes in the apparent dispersion between bursts that can be attributed to frequency-dependent profiles or some other intrinsic burst structure that adds a systematic error to the estimate of DM by up to 1\%. We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}/N_r$\ Mpc$^{-3}$\ yr$^{-1}$, where $N_r$\ is the number of bursts per source over its lifetime. This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts, if the typical FRB repeats on the order of thousands of times during its lifetime.
\end{abstract}

@@

This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was discovered \citep{2014ApJ...790..101S} in data acquired in 2012 as part of the PALFA survey of the Arecibo Observatory \citep{2006ApJ...637..446C, 2015ApJ...812...81L}. In mid 2015, new Arecibo observations revealed a series of bursts at a similar DM and sky position that rules out cataclysmic models for this source \citep{2016Natur.531..202S}. The typical DM measured by early Arecibo observations was 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}, although somewhat higher values have been seen in more recent observations (560.5 pc cm$^{-3}$; Hessels et al., in prep).

@@

This paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Arecibo, Effelsberg, the first station of the Long-Wavelength Array \citep[LWA1; ][]{2013ITAP...61.2540E}, and the Arcminute Microkelvin Imager Large Array \citep[AMI-LA; ][]{2008MNRAS.391.1545Z}. This includes the first simultaneous detection of an FRB at two observatories, between the VLA and Arecibo. If we assume that \frb\ is representative of all FRBs, we can use it to constrain the physical processes at play in the overall FRB population. The repetition of \frb\ also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.

@@

Computational (Jupyter) notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \url{https://github.com/caseyjlaw/FRB121102}. Time cut-out visibility data and calibration products are available at \url{https://doi.org/10.7910/DVN/TLDKXG}. Original VLA visibility data are available under NRAO program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.

@@

In total, 11 Arecibo observations had some simultaneous coverage with the VLA. All of these observations were conducted after the VLA localization, so they were pointing directly at \frb. Three of those observations had simultaneous coverage of VLA bursts and one of those Arecibo observations detected the VLA burst. 
% During the first VLA burst with Arecibo coverage (MJD 57643), the PUPPI 1.4~GHz recording system failed so data were recorded at C band with the mock spectrometer. The C-band observations were recorded at frequencies from 4078 to 4245~MHz and had a sensitivity of 3.6~mJy in 2~ms ($1\sigma$). No detection was made in those Arecibo data. % levels set wrong. useless c-band ao data.
Overall, there were many more bursts detected at Arecibo than with the VLA, including some Arecibo bursts with simultaneous VLA upper limits. A more detailed analysis of those bursts will be presented elsewhere (Michilli et al, in prep).

@@

Overall, the bursts with simultaneous observing coverage are not well described by a power-law model. Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index. The Arecibo and Effelsberg upper limits at 1.4 and 4.5~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.9$ and $\alpha_{3/4.5}<-2.7$. These are consistent with limits from the LWA1 and AMI-LA, which require $\alpha_{0.07/3}>-2.4$\ and $\alpha_{3/15}<1.5$ for bursts on MJD 57643 and 57649 (the brightest VLA bursts with observing coverage), respectively. The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.

@@

\bibliographystyle{yahapj}

@@

% observatories
The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc..
Part of this research was carried out at the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the National Aeronautics and Space Administration.
% systems
This research made use of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
%individuals
CJL is supported by the University of California Office of the President under Lab Fees Research Program Award 237863 and NSF award 1611606. MAM is supported by NSF award 1458952. 
JWTH, CGB, and DM acknowledge support from the European Research Council under the European Union's Seventh Framework Programme (FP/2007-2013) / ERC Grant Agreement nr.\ 337062 (DRAGNET; PI Hessels). JWTH also acknowledges funding from an NWO Vidi fellowship.
SPT acknowledges support from the McGill Astrophysics Fellowship.
KPM's research is supported by the Oxford Centre for Astrophysical Surveys which is funded through the Hintze Family Charitable Foundation. AS gratefully acknowledges support from the European Research Council under grant ERC-2012- StG-307215 LODESTONE. The AMI-LA telescope gratefully acknowledges support from the European Research Council under grant ERC-2012- StG-307215 LODESTONE, the UK Science and Technology Facilities Council (STFC) and the University of Cambridge. 
PS holds a Covington Fellowship at DRAO. 
The LWA1 station is supported by the National Science Foundation under grant 1139974 of the University Radio Observatory program.
VMK acknowledges support from NSERC, CIFAR, the Canada Research Chair Program and from the Lorne Trottier Chair in Astrophysics \& Cosmology.

@@

\software{\emph{rtpipe}, \emph{realfast}, pwkit \citep{2017ascl.soft04001W}}

>>>>

\pdfoutput=1
\documentclass[twocolumn]{aastex61}
\usepackage[space]{grffile}
\usepackage{amsfonts,amsmath,amssymb}
\usepackage{url}
\usepackage{latexsym}
\usepackage{hyperref} 
\usepackage{graphicx}
\usepackage{natbib}
\citestyle{aa}
\usepackage[utf8]{inputenc}
\usepackage{fancyref}
\usepackage{multirow}
\hypersetup{colorlinks=false,pdfborder={0 0 0},}

@@

\title{A Multi-telescope Campaign on FRB 121102: Implications for the FRB Population}
\shorttitle{\frb\ Observing Campaign}
\shortauthors{Law et al.}

@@

\begin{abstract}
We present results of the coordinated observing campaign that made the first subarcsecond localization of a Fast Radio Burst, \frb. During this campaign, we made the first simultaneous detection of an FRB burst by multiple telescopes: the VLA at 3~GHz and the Arecibo Observatory at 1.4~GHz. Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories. We use multi-observatory detections and non-detections of bursts seen at 3~GHz to confirm earlier results showing that burst spectra are not well modeled by a power law. We find that burst spectra are characterized by a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg. We measure significant changes in the apparent dispersion between bursts that can be attributed to frequency-dependent profiles or some other intrinsic burst structure that adds a systematic error to the estimate of DM by up to 1\%. We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}/N_r$\ Mpc$^{-3}$\ yr$^{-1}$, where $N_r$\ is the number of bursts per source over its lifetime. This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts, if the typical FRB repeats on the order of thousands of times during its lifetime.
\end{abstract}

@@

This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}. \objectname[FRB+121102]{FRB 121102}, also known as the ``repeating FRB'', was discovered \citep{2014ApJ...790..101S} in data acquired in 2012 as part of the PALFA survey of the Arecibo Observatory \citep{2006ApJ...637..446C, 2015ApJ...812...81L}. In mid 2015, new Arecibo observations revealed a series of bursts at a similar DM and sky position that rules out cataclysmic models for this source \citep{2016Natur.531..202S}. The typical DM measured by early Arecibo observations was 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}, although somewhat higher values have been seen in more recent observations (560.5 pc cm$^{-3}$; Hessels et al., in prep).

@@

This paper presents an analysis of the spectral properties of VLA bursts implied by detections and nondetections during observing at Arecibo, Effelsberg, the first station of the Long-Wavelength Array \citep[LWA1; ][]{2013ITAP...61.2540E}, and the Arcminute Microkelvin Imager Large Array \citep[AMI-LA; ][]{2008MNRAS.391.1545Z}. This includes the first simultaneous detection of an FRB at two observatories, between the VLA and Arecibo. If we assume that \frb\ is representative of all FRBs, we can use it to constrain the physical processes at play in the overall FRB population. The repetition of \frb\ also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.

@@

Computational (Jupyter) notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \url{https://github.com/caseyjlaw/FRB121102}. Time cut-out visibility data and calibration products are available at \dataset[http://dx.doi.org/10.7910/DVN/TLDKXG]{https://doi.org/10.7910/DVN/TLDKXG}. Original VLA visibility data are available under NRAO program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.

@@

In total, 11 Arecibo observations had some simultaneous coverage with the VLA. All of these observations were conducted after the VLA localization, so they were pointing directly at \frb. Three of those Arecibo observations made no burst detection coincident with the VLA bursts, while one detected the VLA burst. 
% During the first VLA burst with Arecibo coverage (MJD 57643), the PUPPI 1.4~GHz recording system failed so data were recorded at C band with the mock spectrometer. The C-band observations were recorded at frequencies from 4078 to 4245~MHz and had a sensitivity of 3.6~mJy in 2~ms ($1\sigma$). No detection was made in those Arecibo data. % levels set wrong. useless c-band ao data.
Overall, there were many more bursts detected at Arecibo than with the VLA, including some Arecibo bursts with simultaneous VLA upper limits. A more detailed analysis of those bursts will be presented elsewhere (Michilli et al, in prep).

@@

Overall, the burst detections and nondetections show that burst spectra are not well described by a power-law model. Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index. The Arecibo and Effelsberg upper limits at 1.4 and 4.5~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.9$ and $\alpha_{3/4.5}<-2.7$. These are consistent with limits from the LWA1 and AMI-LA, which require $\alpha_{0.07/3}>-2.4$\ and $\alpha_{3/15}<1.5$ for bursts on MJD 57643 and 57649 (the brightest VLA bursts with observing coverage), respectively. The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.

@@

%\bibliographystyle{yahapj}
\bibliographystyle{apj}

@@

% observatories
The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc..
Part of this research was carried out at the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the National Aeronautics and Space Administration.
% systems
This research made use of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
%individuals
CJL is supported by the University of California Office of the President under Lab Fees Research Program Award 237863 and NSF award 1611606. MAM is supported by NSF award 1458952. 
JWTH, CGB, and DM acknowledge support from the European Research Council under the European Union's Seventh Framework Programme (FP/2007-2013) / ERC Grant Agreement nr.\ 337062 (DRAGNET; PI Hessels). JWTH also acknowledges funding from an NWO Vidi fellowship.
SPT acknowledges support from the McGill Astrophysics Fellowship.
KPM's research is supported by the Oxford Centre for Astrophysical Surveys which is funded through the Hintze Family Charitable Foundation. AS gratefully acknowledges support from the European Research Council under grant ERC-2012- StG-307215 LODESTONE. The AMI-LA telescope gratefully acknowledges support from the European Research Council under grant ERC-2012- StG-307215 LODESTONE, the UK Science and Technology Facilities Council (STFC) and the University of Cambridge. 
PS holds a Covington Fellowship at DRAO. 
MWA was a participant in the 2016 Research Experience for Undergraduates in Astronomy and Astrophysics at Cornell University program, supported by grant NSF/AST-1156780.
The LWA1 station is supported by the National Science Foundation under grant 1139974 of the University Radio Observatory program.
VMK acknowledges support from NSERC, CIFAR, the Canada Research Chair Program and from the Lorne Trottier Chair in Astrophysics \& Cosmology.

@@

\software{\emph{rtpipe}, \emph{realfast}, pwkit \citep{2017ascl.soft04001W}, emcee \citep{2013PASP..125..306F}}
